\classheader{Wizard}{
    \textbf{Luck}: A wizard’s Luck modifier applies to rolls for corruption and mercurial magic. \\
    \textbf{Languages}: A wizard knows two additional languages for every point of Int modifier. \\
    \textbf{Weapon training}: A wizard is trained in the use of the dagger, longbow, longsword, shortbow, short sword, and staff. Wizards rarely wear armor, as it hinders spellcasting. \\
    \textbf{Magic}: Wizards cast spells by making a spell check. A wizard's spell check is usually 1d20 + intelligence modifier + level. \\
    \textbf{Spellburn}: Wizards may sacrifice ability scores for bonuses to spell checks. For every ability point they expend, the wizard adds +1 to his spell check. Ability scores lost in this way return at a rate of 1 per day that spellburn has not been inflicted. Other sacrifices can also net casting bonuses, at a rate of +1 per 500gp. \\
    % \textbf{Mercurial Magic}: The effect of a magical spell varies according to who casts it. When you learn a new spell, roll on table 5-2 (pg 111) and adjust by your luck modifier x 10\%. \\
    \textbf{Corruption}: Low-level wizards are powerful. High-level wizards fear for their souls. Magical corruption results from natural 1s on spell checks, such as misfire and/or corruption. Corruption effects are permanent but modified by the wizard's luck score.\\
}
\draw (1.1\foldwidth, .3\textheight) rectangle (1.9\foldwidth, .13\foldwidth) node[pos=.5,yshift=.13\textheight, above] {\textbf{Corruption effects}};
